\cvsection{Publications}

\publication{Preprint}{S$^3$: Structured Sparsity Specification\link{https://arxiv.org/abs/2604.11315}}{Ghriss, A.}
\divider
\vspace{-1pt}

\publication{AISTATS '26}{Beyond Spectral Clustering: Probabilistic Cuts for Differentiable Graph Partitioning\link{https://arxiv.org/abs/2511.02272}}{Ghriss, A. \quad \textit{\textbf{Outstanding Paper Award}, CU Boulder CS Dept.}}
\divider
\vspace{-1pt}

\publication{MusML ICML '25}{Crowdsourced Information Authentication: A Graph-based Model from the Science of Hadith\link{}}{Ghriss, A. \quad \textit{Oral presentation.}}
\divider
\vspace{-1pt}

\publication{AISTATS '25}{Deep Clustering via Probabilistic Ratio-Cut Optimization\link{https://arxiv.org/abs/2502.03405}}{Ghriss, A., Monteleoni, C. \quad \textit{\textbf{Outstanding Paper Award}, CU Boulder CS Dept.}}
\divider
\vspace{-1pt}

\publication{ASCE '24}{Predicting Serious Injury and Fatality Exposure using Machine Learning in Construction Projects\link{https://ascelibrary.org/doi/full/10.1061/JCEMD4.COENG-13741}}{Oguz Erkal, E.D., Hallowell, M.R, Ghriss, A., Bhandari, S.}
\divider
\vspace{-1pt}

\publication{ICASSP '22}{Sentiment-aware ASR Pre-training for Enhanced Speech Emotion Recognition\link{https://arxiv.org/abs/2201.11826}}{Ghriss, A., Yang, B., Rozgic, V., Shriberg, E., Wang, C.}
\divider
\vspace{-1pt}

\publication{NeuroImage '22}{Insights from an Autism Imaging Biomarker Challenge: Promises and Threats to Biomarker Discovery\link{https://www.sciencedirect.com/science/article/pii/S1053811922002981}}{Traut, N., et al. (incl. Ghriss, A.) \quad \textit{Best ML model among participants.}}
\divider
\vspace{-1pt}

\publication{RIKEN AIP '18}{Reinforcement Learning with Options and State Representation\link{https://arxiv.org/abs/2403.10855}}{Ghriss, A., Sugiyama, M., Lazaric, A.}

\newpage
\cvsection{Selected Open-Source Software}
\vspace{4pt}

\cvproject{PGCuts}{Differentiable graph cuts with GPU-accelerated hypergeometric kernels; sklearn-compatible API.}{\footnotesize\href{https://github.com/ayghri/pgcuts}{github.com/ayghri/pgcuts} \; \textbullet \; \href{https://pgcuts.readthedocs.io}{pgcuts.readthedocs.io}}
\divider

\cvproject{SparseKit}{Structured sparsity specification (S$^3$) toolkit for carving LLM weights under user-defined patterns.}{\footnotesize\href{https://github.com/ayghri/sparsekit}{github.com/ayghri/sparsekit} \; \textbullet \; \href{https://sparsekit.readthedocs.io}{sparsekit.readthedocs.io}}
\divider

\cvproject{Qwantize}{Optimal quantization for block-scaled low-precision formats (NVFP4, MXFP4).}{\footnotesize\href{https://github.com/ayghri/qwantize}{github.com/ayghri/qwantize} \; \textbullet \; \href{https://qwantize.readthedocs.io}{qwantize.readthedocs.io}}
\divider

\cvproject{Tritonix}{Triton GPU kernels with an optimized autotuning framework.}{\footnotesize\href{https://github.com/ayghri/tritonix}{github.com/ayghri/tritonix}}
\divider

\cvproject{Sphedron}{Refinable polyhedral meshes on the sphere for GNN-based geospatial ML.}{\footnotesize\href{https://github.com/ayghri/sphedron}{github.com/ayghri/sphedron} \; \textbullet \; \href{https://sphedron.readthedocs.io}{sphedron.readthedocs.io}}

\vspace{0.6em}
\cvsection{Service \& Talks}
\vspace{4pt}
\small
\begin{itemize}
\setlength{\itemindent}{0.9em}
    \item \textbf{Reviewer:} ICLR 2025 \; \textbullet \; ICML 2025, 2026 \; \textbullet \; NeurIPS 2025
    \item \textbf{Tutorial Chair:} ``Associative Memories'', ICML 2025
    \item \textbf{Oral Presentation:} \textit{Crowdsourced Information Authentication: A Graph-based Model from the Science of Hadith}, MusML Workshop, ICML 2025
    \item \textbf{Workshop Instructor:} \textit{GPU Programming Workshop} --- CS Graduate Professional Development Club, CU Boulder, Spring '26. Hands-on intro to parallel execution, thread/warp behavior, fused kernels, and Triton. \href{https://github.com/ayghri/gpuwork}{github.com/ayghri/gpuwork}
    \item \textbf{Guest Lectures:} \textit{Introduction to Machine Learning} --- ASEN 5307 Engineering Data Analysis Methods, CU Boulder (2 lectures in Fall '24, 2 in Fall '25)
\end{itemize}

\vspace{0.6em}
\cvsection{Awards \& Honors}
\vspace{4pt}
\small
\begin{itemize}
\setlength{\itemindent}{0.9em}
    \item \textbf{Outstanding Paper Award}, CU Boulder CS Dept.\ --- for \textit{Beyond Spectral Clustering: Probabilistic Cuts for Differentiable Graph Partitioning} (AISTATS '26).
    \item \textbf{Outstanding Paper Award}, CU Boulder CS Dept.\ --- for \textit{Deep Clustering via Probabilistic Ratio-Cut Optimization} (AISTATS '25).
    \item \textbf{Best Work-in-Progress Award}, CU Boulder CS Dept.\ Expo, Fall '25 --- for work on structured sparse training (S$^3$).
    \item \textbf{Outstanding Teaching Assistant Award}, CU Boulder CS Dept., '22.
\end{itemize}
