\cvsection{Work Experience}
\begin{minipage}[t]{0.49\linewidth}

\cvwork{Teaching Assistant}{Aug 2021 -- Present}{CU Boulder, Computer Science}
{
\footnotesize
\begin{itemize}
\item Graduate Machine Learning (CSCI 5266 / 5622): Fall '21, Fall '23, Spring '26.
\item Undergraduate Machine Learning (CSCI 4266), '22--'23; guest instructor for the Reinforcement Learning module.
\item Tutorials on Small Language Models (Fall '23).
\item \textbf{Outstanding Teaching Assistant Award}, '22.
\end{itemize}
\vspace{-5pt}
}
\divider

\cvwork{Graduate Research Assistant}{Jan 2024 -- Dec 2025}{CIRES, CU Boulder}
{
\footnotesize
\begin{itemize}
\item GNN-based emulators for climate-model dynamics on refinable spherical meshes; released as the \textit{Sphedron} library.
\end{itemize}
\vspace{-5pt}
}
\divider

\cvwork{Visiting Researcher}{Jun -- Aug 2023}{Inria, Paris}
{
\footnotesize
\begin{itemize}
\item Deep learning for optimization over discrete sets.
\end{itemize}
\vspace{-5pt}
}

\end{minipage}
\hfill
\rule[-19em]{0.05mm}{19em}
\hfill
\begin{minipage}[t]{0.49\linewidth}

\cvwork{Applied Scientist Intern}{May -- Aug 2022}{Amazon Alexa Paralinguistics, Cambridge}
{
\footnotesize
\begin{itemize}
\item Speaker identification and paralinguistic speech-emotion modeling on conversational audio.
\end{itemize}
\vspace{-5pt}
}
\divider

\cvwork{Applied Scientist Intern}{May -- Aug 2021}{Amazon Alexa Edge-ML, Cambridge}
{
\footnotesize
\begin{itemize}
\item Sentiment-aware ASR pre-training for on-device speech-emotion recognition (ICASSP '22).
\end{itemize}
\vspace{-5pt}
}
\divider

\cvwork{Software Engineer, PhD Intern}{Jun -- Aug 2020}{Google, Boulder}
{
\footnotesize
\begin{itemize}
\item Deep learning for air-quality prediction from satellite imagery (Google Earth Engine).
\end{itemize}
\vspace{-5pt}
}
\divider

\cvwork{Research Intern}{Apr -- Sep 2018}{RIKEN Advanced Intelligence Project, Tokyo}
{\footnotesize
\begin{itemize}
\item Hierarchical deep reinforcement learning with options and learned state representations.
\end{itemize}
\vspace{-5pt}
}
\end{minipage}
